Robust Spectroscopic Inference with Imperfect Models

### 2014-09-07 tex/paper.tex
Last commit before rewriting the C/cython routines

\citet{torres12} originally acquired these data in an effort to measure the WASP-14 stellar 
properties, and thereby better constrain the parameters of the transiting exoplanet it hosts.  To 
that end, they employed the {\tt MOOG} and {\tt SPC} approaches outlined in Section 
\ref{sec:intro}.  Their analysis was performed in two ways, with the surface gravity treated as a 
free parameter or assumed to be fixed (to $\log g = 4.29$) based on an inference of the mean 
stellar density from the exoplanet transit depth and a comparison of WASP-14 photometry to stellar 
evolution models in the H-R diagram \citep{joshi09}.  Only parameter inferences from the latter 
assumption were reported.  The {\tt MOOG} analysis employed \citet{kurucz93} atmospheres to 
synthesize a suite of individual \ion{Fe}{1} and \ion{Fe}{2} lines in the $\sim$4300--6750\AA\ 
region, whose equivalent widths were compared with the TRES measurements in a simple least-squares 
sense.  This approach suggests that $T_{\rm eff} = 6150\pm75$\,K and $[{\rm Fe/H}] = 
-0.34\pm0.10$\,dex.  The {\tt SPC} analysis relied on a direct comparison between three TRES 
spectral orders covering $\sim$5100-5400\,\AA\ and synthetic spectra from the {\sc CfA/Kurucz} 
library; it indicates $T_{\rm eff} = 6507\pm50$\,K, $[{\rm Fe/H}] = -0.15\pm0.08$\,dex, and $v \sin 
i = 3.9\pm0.5$\,km s$^{-1}$.  It is worth noting that these parameter inferences represent an 
average of those determined from four distinct TRES datasets, such that the uncertainties reflect 
the systematic spread between the best-fit parameter values. \comm{This is something we need to 
discuss more with Dave and Willie.}

@@

\comm{Should make note of surveys like the ESA/Gaia program, SEGUE, RAVE, too.  Probably need to 
include citations to each.  Also, I think HERMES is really GALAH, right?  If not, it should be 
linked to that, since there is a popular Herschel HERMES program that will confuse people...}

\acknowledgments  List your acknowledgments (don't forget anyone!).  I can think of: 
Foreman-Mackey, Hogg, people on Johnson's group?, Lars?, TRES archive people?  You might want to 
acknowledge your NSF Fellowship here, and the Smithsonian Institution (how you're being paid now), 
for funding.  Figures \ref{fig:Kurucz_posterior}, \ref{fig:PHOENIX_posterior}, and \ref{fig:Gl51_posterior} were generated with \texttt{triangle.py} \citep{foreman-mackey14}.

>>>>

\citet{torres12} originally acquired these data in an effort to measure the WASP-14 stellar 
properties, and thereby better constrain the parameters of the transiting exoplanet it hosts.  To 
that end, they employed the {\tt MOOG} and {\tt SPC} approaches outlined in Section 
\ref{sec:intro}.  Their analysis was performed in two ways, with the surface gravity treated as a 
free parameter or assumed to be fixed (to $\log g = 4.29$) based on an inference of the mean 
stellar density from the exoplanet transit depth and a comparison of WASP-14 photometry to stellar 
evolution models in the H-R diagram \citep{joshi09}.  Only parameter inferences from the latter 
assumption were reported.  The {\tt MOOG} analysis employed \citet{kurucz93} atmospheres to 
synthesize a suite of individual \ion{Fe}{1} and \ion{Fe}{2} lines in the $\sim$4300--6750\AA\ 
region, whose equivalent widths were compared with the TRES measurements in a simple least-squares 
sense.  This approach suggests that $T_{\rm eff} = 6150\pm75$\,K and $[{\rm Fe/H}] = 
-0.34\pm0.10$\,dex.  The {\tt SPC} analysis relied on a direct comparison between three TRES 
spectral orders covering $\sim$5100-5400\,\AA\ and synthetic spectra from the {\sc CfA/Kurucz} 
library; it indicates $T_{\rm eff} = 6507\pm50$\,K, $[{\rm Fe/H}] = -0.15\pm0.08$\,dex, and $v \sin 
i = 3.9\pm0.5$\,km s$^{-1}$.  It is worth noting that these parameter inferences represent an 
average of those determined from four distinct TRES datasets, such that the uncertainties reflect 
the systematic spread between the best-fit parameter values. 
%\comm{This is something we need to discuss more with Dave and Willie.}

@@

%\comm{Should make note of surveys like the ESA/Gaia program, SEGUE, RAVE, too.  Probably need to 
%include citations to each.  Also, I think HERMES is really GALAH, right?  If not, it should be 
%linked to that, since there is a popular Herschel HERMES program that will confuse people...}

%\acknowledgments  List your acknowledgments (don't forget anyone!).  I can think of: 
%Foreman-Mackey, Hogg, people on Johnson's group?, Lars?, TRES archive people?  You might want to 
%acknowledge your NSF Fellowship here, and the Smithsonian Institution (how you're being paid now), 
%for funding.  Figures \ref{fig:Kurucz_posterior}, \ref{fig:PHOENIX_posterior}, and \ref{fig:Gl51_posterior} were generated with \texttt{triangle.py} \citep{foreman-mackey14}.
%
